---
title: "visualisations1"
author: "MN"
date: "03/05/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualisation

Basic plots
*   Histogram
*   Bar / Line Chart
*   Box plot
*   Scatter plot

## Histogram
-  plot that breaks the data into bins (or breaks) and shows frequency distribution of these bins
```{r}
library(RColorBrewer)
data(VADeaths)
hist(VADeaths,breaks=10, col=brewer.pal(3,"Set3"),main="Set3 3 colors")
hist(VADeaths,breaks=3 ,col=brewer.pal(3,"Set2"),main="Set2 3 colors")
hist(VADeaths,breaks=7, col=brewer.pal(3,"Set1"),main="Set1 3 colors")
hist(VADeaths,,breaks= 2, col=brewer.pal(8,"Set3"),main="Set3 8 colors")
hist(VADeaths,col=brewer.pal(8,"Greys"),main="Greys 8 colors")
hist(VADeaths,col=brewer.pal(8,"Greens"),main="Greens 8 colors")
```

## Line Plots



```{r}
plot(AirPassengers,type="l")  #Simple Line Plot
```
## BarPlots



```{r}
barplot(iris$Petal.Length) #Creating simple Bar Graph
barplot(iris$Sepal.Length,col  = brewer.pal(3,"Set1"))
barplot(table(iris$Species,iris$Sepal.Length),col  = brewer.pal(3,"Set1")) #Stacked Plot
```

## Boxplot
- the 25th percentile, the median, the 75th percentile and the maximum. 
- useful for visualising the spread of data
```{r}
boxplot(iris$Petal.Length~iris$Species) #Creating Box Plot between two variable
```

```{r}
data(iris)
par(mfrow=c(2,2))
boxplot(iris$Sepal.Length,col="red")
boxplot(iris$Sepal.Length~iris$Species,col="red")
```


```{r}
boxplot(iris$Sepal.Length~iris$Species,col=heat.colors(3))
boxplot(iris$Sepal.Length~iris$Species,col=topo.colors(3))
```

## Scatter plot
Help visualise multiple variables

```{r}
plot(x=iris$Petal.Length) #Simple Scatter Plot
plot(x=iris$Petal.Length,y=iris$Species) #Multivariate Scatter Plot
```

